Notes and approaches to OCR

### 2020-08-17 outputs/documents/paper.Rmd
Add PyTesseract to the list

**(Diego: please add options here in a table and then a brief write-up of each - costs, access, technical requirements, etc.)**

>>>>

| OCR Tool                             | Company	 | Type           |	Pricing |	Tech Requierements |
| ------------------------------------ | --------- | -------------- | ------- | ------------------ |
| Azure Cognitive Services (OCR)       | Microsoft | API		        |         |                    |
| Amazon Rekognition	                 | Amazon	   | API		        |         |                    |
| Tesseract		                         |           | R library      | Free	  |                    |
| PyTesseract                          |           | Python Library | Free    |                    |
| OpenCV		                           |           | Python Library | Free	  |                    |
| Watson Visual Recognition	           | IBM	     | API		        |         |                    |
| Kraken		                           |           | Python Library	| Free	  |                    |
| Google Vision (for Text recognition) | Google	   | API		        |         |                    |
| SwiftOCR	(iOS)                      | Apple	   | Swift Library  |         |                    | 		
| Amazon Textract	                     | Amazon	   | API		        |         |                    |
|	Tensorflow                           | Google    | Python Library | Free    |                    |
